Northern Pikeminnow Predation on Juvenile Chinook Salmon in Deadwater Slough, Salmon River, Idaho and Potential Impacts to Local Populations

### 2021-12-29 analysis/paper/paper.Rmd
minor edits to acknowledgements

The authors extend much appreciation to the many volunteers who assisted with field efforts including collaborators from the Bureau of Reclamation, Idaho Office of Species Conservation, Idaho Deparment of Fish and Game, and the Lemhi Regional Land Trust, among others. Special thanks to Chelsea Welke, Tulley Mackey, Jared Barker, and Brian Hamilton for their help in the field. Special thanks to Caitlin Alcott and Inter-Fluve for their administrative support and guidance. Funding for this study was provided by the Bureau of Reclamation, Pacific Northwest Regional Office (contract No. 140R1021F0018) with assistance from the Idaho Office of Species Conservation.

>>>>

The authors extend much appreciation to the many volunteers that assisted with field efforts including collaborators from the Bureau of Reclamation, Idaho Governor’s Office of Species Conservation, Idaho Department of Fish and Game, and the Lemhi Regional Land Trust, among others. Special thanks to Jared Barker, Brian Hamilton, Tulley Mackey, and Chelsea Welke for their help in the field. We further appreciate the administrative support and guidance from Caitlin Alcott and Inter-Fluve. Funding for this study was provided by the Bureau of Reclamation, Pacific Northwest Regional Office (contract No. 140R1021F0018) with assistance from the Idaho Governor’s Office of Species Conservation.
